---
title: "p8105_hw5_wm2460"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

## Problem 2
```{r raw}
homicides_df = read_csv("./data/homicide-data.csv")
```

#### Describe the raw data

In the `homicides_df` dataset, there are `r nrow(homicides_df)` observations and `r ncol(homicides_df)` variables. The variables in this dataset include `r colnames(homicides_df)`. 

```{r summarize}
homicides_new = homicides_df %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, state, sep = "_"),
         status = 
           case_when(disposition == "Closed without arrest" ~ "unsolved",
                     disposition == "Open/No arrest" ~ "unsolved",
                     disposition == "Closed by arrest" ~ "resolved")) 

summarize_df = homicides_new %>% 
  group_by(city_state) %>% 
  summarize(total = n(),
            unsolved = sum(status == "unsolved")) 

summarize_df
```

#### Using `prop.test` for Baltimore, MD
```{r baltimore}
prop.test(summarize_df %>% filter(city_state == "Baltimore_MD") %>%
            pull(unsolved), 
          summarize_df %>% filter(city_state == "Baltimore_MD") %>%
            pull(total)) %>% 
  broom::tidy()

# save the output of prop.test as an R object
prop.test(summarize_df %>% filter(city_state == "Baltimore_MD") %>%
            pull(unsolved), 
          summarize_df %>% filter(city_state == "Baltimore_MD") %>%
            pull(total)) %>% 
  broom::tidy() %>% 
  saveRDS(., "./data/Baltimore_prop_test.rds")
```

#### Using `prop.test` for each cities
```{r all_cities}
all_cities = summarize_df %>% 
  mutate(prop_tests = map2(.x = unsolved, .y = total, ~ prop.test(x = .x, n = .y)),
         tidy_df = map(.x = prop_tests, ~ broom::tidy(.x))) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_df) %>% 
  select(city_state, estimate, conf.low, conf.high)

all_cities
```

#### A plot that shows the estimates and CIs for each city 
```{r plot}
all_cities_plot = all_cities %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

all_cities_plot
```


## Problem 3

#### Set up the simulation
```{r sim_1}
sim_1 = function(n = 30, mu = 0, sigma = 5) {
     x = rnorm(n, mean = mu, sd = sigma)
     t_test = t.test(x, conf.int = 0.95) %>% broom::tidy()
     
     t_test
}

p3_df = vector("list", 1000)

for (i in 1:1000) {
  p3_df[[i]] = sim_1()
}

p3_df %>% 
  bind_rows() %>% 
  head()
```

#### Simulation for different mu
```{r sim_2}
sim_2 = function(set){
  
  p3_df = vector("list", 1000)
  for (i in 1:1000) {
     p3_df[[i]] = sim_1(mu = set)
  }
  
  power = 
    p3_df %>% 
    bind_rows() %>% 
    janitor::clean_names() %>% 
    select(estimate, p_value) %>% 
    filter(p_value < 0.05) %>% 
    count()
  
  power
  
}

test_power =
  tibble(mus = c(0, 1, 2, 3, 4, 5, 6),
         reject_time = map(mus, sim_2)) %>%  
  unnest(reject_time) %>% 
  mutate(power = n/1000)
```

#### A plot between the power of the test and the true value of μ
```{r power_plot}
power_plot = test_power %>% 
  ggplot(aes(x = mus, y = power)) +
  geom_point(aes(color = mus), size = 2) +
  geom_line(alpha = 0.3) +
  labs(x = "True value of μ",
       y = "Power of the test")

power_plot
```

From the plot, we can see clearly that the power of the test increase as the true value of μ increase. Therefore, as the effect size (i.e., the true value of μ) increase, power increases. 

#### A plot showing the average estimate of μ^ and the true value of μ 
```{r average_plot}
sim_3 = function(n = 30, mu = 0, sigma = 5) {
     sim_data = tibble(x = rnorm(n, mean = mu, sd = sigma),)
     
     sim_t_test = t.test(pull(sim_data,x), conf.int = 0.95) %>% 
              broom::tidy() %>% 
              janitor::clean_names() %>% 
              select( p_value)
     
     sim_data %>% 
     summarize(mu_hat_all = mean(x),
               mu_hat_rej = case_when(
                 pull(sim_t_test, p_value) < 0.05 ~ mean(x),
                 pull(sim_t_test, p_value) >= 0.05 ~ as.numeric("")))
}

sim_4 = function(set){
  mu_hat = vector("list", 1000)
  for (i in 1:1000) {
     mu_hat[[i]] = sim_3(mu = set)
     }
  
  mu_hat %>% 
    bind_rows() %>% 
    summarize(all = mean(mu_hat_all, na.rm = TRUE),
              reject = mean(mu_hat_rej, na.rm = TRUE))
}

average_muhat =
  tibble(true_mu = c(0, 1, 2, 3, 4, 5, 6),
         muhat = map(true_mu, sim_4)) %>%  
  unnest(muhat) %>% 
  pivot_longer(all:reject,
               names_to = "samples",
               values_to = "average")

all_plot = average_muhat %>% 
  filter(samples == "all") %>% 
  ggplot(aes(x = true_mu, y = average)) +
  geom_point(size = 2) +
  geom_line()

all_plot

reject_plot = average_muhat %>% 
  filter(samples == "reject") %>% 
  ggplot(aes(x = true_mu, y = average)) +
  geom_point(size = 2) +
  geom_line()

reject_plot

together_plot = average_muhat %>% 
  ggplot(aes(x = true_mu, y = average, group = samples)) +
  geom_point(aes(color = samples), size = 2) +
  geom_line(alpha = 0.5)

together_plot
```


When the true mu is less than 4, the sample average of μ^ across tests for which the null is rejected is not approximately equal to the true value of μ. However, if the true mu is 4, 5, or 6, the sample average of μ^ across tests for which the null is rejected is approximately equal to the true value of μ. 


